---
title: "Sample Apps Source Code"
author: "NEST CoreDev Team"
date: "2023-02-08"
output: "rmarkdown::html_document"
vignette: >
  %\VignetteIndexEntry{Sample Apps Source Code}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{css, echo=FALSE}
pre {
  max-height: 800px;
  overflow-y: auto;
}

pre[class] {
  max-height: 400px;
}
```

The sample apps serve as a starting template for your specific `teal` app.

Please always use the sample apps as a starting point for your applications, as we keep updating the NEST packages without necessarily backwards compatible releases.

You need to save the source code in a file `app.R` to begin developing your `teal` application.

## Sample app source code

Source code for all available sample apps in this gallery is available below.

```{r results='asis', echo=FALSE}
library(teal.gallery)

posit_connect_url <- Sys.getenv("POSIT_CONNECT_SERVER")
nest_release <- Sys.getenv("VANITY_URL_SUFFIX")
if (posit_connect_url == "") posit_connect_url <- "https://shinyapps.io"
if (nest_release == "") nest_release <- "main"

x <- lapply(
  list_apps(),
  function(app) {
    deployed_app_link <- paste(posit_connect_url, paste("NEST", app, nest_release, sep = "_"), sep = "/")
    cat(paste("###", app, "\n"))
    cat(paste("Deployed app:", deployed_app_link, "\n"))
    cat("```r")
    get_app_code(app)
    cat("```\n\n")
  }
)
```

## Viewing sources on your workstation

To view the source code for any of these sample apps on your workstation, simply:

* Install the `teal.gallery` package locally.
* Pick an app whose source code you want to view from this list:
```{r}
teal.gallery::list_apps()
```
* View the source of the sample by running:
```{r eval=FALSE}
teal.gallery::get_app_code("<app name>")
```
