---
title: "Getting Started with teal.gallery"
author: "NEST CoreDev Team"
date: "2023-02-08"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with teal.gallery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`teal.gallery` is an R package which contains a set of `teal` applications which can be run and their source code can be extracted and used as a starting point for your own `teal` applications.

```{r setup, eval = FALSE}
library(teal.gallery)

# get the names of the apps in the gallery
available_apps <- list_apps()
print(available_apps)

# launch the first app in the gallery
launch_app(available_apps[1])

# get the source code of this app
code <- get_app_code(available_apps[1])

# code can be saved into a file
writeLines(code, con = file("app.R"))
```

Installing `teal.gallery` does not install the packages required to run the apps in the gallery. When you run `launch_app` the function checks if the requested app's dependencies are available and if not an error is shown stating which packages need to be installed.
